Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

Aatehistoria ja digitaalisten aineistojen mahdollisuudet ([Tolonen &
Lahti (2015) - add to
bib](http://www.ennenjanyt.net/2015/08/aatehistoria-ja-digitaalisten-aineistojen-mahdollisuudet/)).

Embed citations from bib files with `r citep(bib[["lahti14natcomm"]])`.

@@

>>>>

Aatehistoria ja digitaalisten aineistojen mahdollisuudet `r citep(bib[["Tolonen15EnnenNyt"]])`

@@

You can cite with the DOI (the citation info will then be collected automatically): `r citep("10.18352/lq.10112")` or alternatively add new references to the [bib
file](bibliography.bib) and then cite using the key with
`r citep(bib[["Lahti15LIBER"]])`. Such citations will be automatically
numbered and collected in references section.
